micro data server using raspberry pi

### 2015-02-23 paper/paper.tex
changes

\section{Motivation}
Today there are many cloud services. This amount of cloud computing services is increasing fast \cite{armbrust:2009}.  Despite the attention
from the research community, research and development of
Cloud Computing services is still in it's childhood\cite{tso:2013}. 
In this research the Raspberry Pi cloud services will be investigated. A reason for this is that the density of servers has increased a lot in the past\cite{density}. There are new technologies such as for example the ARM processor. Many companies want to explore the possibilities of for example the Raspberry Pi and his ARM Processor. Some data centers even offer some cloud computing using the Raspberry Pi. A reason for this is the co-location and the low power usage of a Raspberry Pi\cite{hosting,Pcextreme}.  A Raspberry Pi has a power usage between the 3-5 Watt. A normal server has a power usage between the 75 and 150 watt \cite{Powerusage}. This could mean that it is better to use a Raspberry Pi for specific small tasks that do not demand a whole server. During this research I want to further investigate the performance of the Raspberry pi as a server.  A Raspberry Pi can be the small data center for the future \cite{tso:2013}. The Raspberry is a rather cheap device for 35 euros. This makes it cheaper to do research in compared to a normal server. This is also the mean reason why the Raspberry pi was ones created. The current versions of the Raspberry Pi cannot perform the task of a large scale x86 server \cite{tso:2013}. Building a cloud like this can be a cost effective scale model\cite{tso:2013}. It's a ideal testbed for testing distributed software. During this research we will investigate the performance of a raspberry pi as a video streamer to other computers. The reason I want to investigate it with video streaming is because this demands a lot of bandwidth from the network and could be one of the first things that should be improved.

\section{Specific problem}

Today a lot of people watch their movies online using video streaming. 
The Netherlands have for example one million subscribers for Netflix \cite{volkskrant}. Netflix is a video streaming service that makes HD movies watching possible. For this Netflix makes use of a content distribution network (CDN). On the internet
this is also known as a on demand service \cite{Adhikari:2012}. Netflix makes use of
MPEG-DASH a protocol that makes streaming over http possible \cite{martin:2013}. The problem is that Netflix is responsible for  29.7\% of the peak downstream traffic in US  \cite{Adhikari:2012}. In the Netherlands more and more users are making use of video streaming as Youtube and Netflix.  In this research we want to investigate if it is possible to make small micro data centers with raspberry pi's. This research will try to find out how this cloud works. There will be taken a look in for example the load balancing of video streaming. In this way it can be possible to see improvements that can be made in the load balancing so that the servers can be used more efficient. This is also build to learn more from load balancing and a computer cluster. This can be really useful, because nowadays it's still done on relatively expensive servers.

\section{Research questions}
The main research question
is: What is the performance of a raspberry pi load balancing service using video streaming?

In order to come to a good answer we need to  research several things

build our own Raspberry Pi setup. There needs to be decided with which benchmark the performance will be measured. After we have measured the performance we can see

\subsection{What is small scale cloud computing?}
In this research I want to do some small scale cloud computing. The main motivation behind is is that it is ways to expensive to simulate large scale cloud computing. Another reason is the Co-location that can be used with small scale cloud computing. Because of this it could be better in executing small tasks. Small scale cloud computing is cloud computing with smaller computation amounts than normal. More motivation is that it does not use a lot of space and power. 
Resources I could use for small scale cloud computing:
\cite{Pcextreme,armbrust:2009,richardson:2012,abrahamsson:2013,southampton}

\subsection{What is cloud video streaming}
There are a lot of cloud services nowadays. These include a webserver, a DNS server, a chat server, a mail server, a vpn server or a monitoring server or even a video streaming service. 
Today a lot of people watch their movies online using video streaming. The netherlands have for example one million subscribers for Netflix \cite{volkskrant}. Netflix is a video streaming service that makes HD movies watching possible. For this Netflix makes use of a content distribution network (CDN). On the internet this is also known as a on demand service. They make use of amazon its AWS with a AWS cloud, Amazon simpleDB , S3 and cassandra for file storage \cite{Adhikari:2012}. Netflix makes use of MPEG-DASH a protocol that makes streaming over http possible. In this research I want to investigate more in the video streaming as a cloud service. 
To investigate this I want to make a experimentation cloud with Raspberry Pi's to see if it will work as a cloud. 
Resources I could use for cloud video streaming:
\cite{g-streamer,raspberry-video,video-1080p, plissonneau:2012}

\subsection{What kind of different load balancing techniques are there?}
In distributed servers it is very important that good load balancing takes place. For this reason I want to further investigate in what kind of load balancing techniques there are. 
Resources I could use for load balancing:
\cite{nginx-load-balancing,nginx-load-balancing-2,computer-networking,wolf:1997,load-balancing}

\subsection{Is it reachable to build small personal Raspberry Pi clouds for services}
With this subquestion I want to find out if it is possible to let users have small Raspberry Pi servers I also want to know what the performance of this small Raspberry Pi cloud is. 
Resources:
\cite{Pcextreme,nginx-load-balancing,nginx-load-balancing-2}

\subsection{Is it possible to improve load balancing using small scale Raspberry Pi's}
For this research I want to investigate if it is possible to do more research in the 
load balancing techniques that can be used in a raspberry pi. A example of this would be the round robin protocol.
Resources:
\cite{nginx-load-balancing,nginx-load-balancing-2}

@@

\section{Planning}

\begin{table}[H]
	\centering \caption{Planning}
\begin{tabular}{|c|c|c|} \hline
		\textbf{Week} & \textbf{Date} & \textbf{Activity} \\ \hline 
		6-9& 6 Feb. -27 Feb& Collect literature and software\\ \hline 
		10& 2 March - 9 March& Deadline peer review and proposal \\ \hline
		12& 16 March -22 March & \textbf{Deadline proposal} \\ \hline
		13 & 23 March -30 March &  \textbf{Accept Reject proposal} \\ \hline
		10-14& 2 March 12 April& Start building test environment \\ \hline
		14& 6 April - 12 April& Answer subquestion 1  \\ \hline
		15& 13 April - 20 April& Answer subquestion 2\\ \hline
		16& 21 April - 28 April& Answer subquestion 3\\ \hline
		14-16 & 6 April - 28 April & working on test environment \\ \hline
		17& 1 May - 7 May & Answer subquestion 4 \\ \hline
		18& 4 May-10 May& conclusion and check coherency \\ \hline
		19& 11 May-18 May& Finalize paper \\ \hline
		22& 1 June-7 June&  \textbf{Deadline paper} \\ \hline
		26 &22 June - 26 June & \textbf{Conference} \\ \hline
		\end{tabular}

		\label{tab:planning}
\end{table}
Here above is the table~\ref{tab:planning}. The main research question is split up into several sub questions. These subquestions have each one week for answering. After that there is time to write the conclusion and answer the main question. Then there is still some time left to finalize the paper.

@@

>>>>

\section{Introduction}
Today there are many cloud services. This amount of cloud computing services is increasing fast \cite{armbrust:2009}.  Despite the attention
from the research community, research and development of Cloud Computing services is still in it's childhood\cite{tso:2013}. 
In this research the Raspberry Pi cloud services will be investigated. A reason for this is that the density of servers has increased a lot in the past\cite{density}. There are new technologies such as for example the ARM processor. Many companies want to explore the possibilities of for example the Raspberry Pi and his ARM Processor. Some data centers even offer some cloud computing using the Raspberry Pi. A reason for this is the small location that the Raspberry Pi needs, and the low power usage of a Raspberry Pi\cite{hosting,Pcextreme}.  A Raspberry Pi has a power usage between the 3-5 Watt. A normal server has a power usage between the 75 and 150 watt \cite{Powerusage}. This could mean that it is better to use a Raspberry Pi for specific small tasks that do not demand a whole server. During this research there will be a investigation on the performance of the Raspberry pi as a server.  A Raspberry Pi can be the small data center for the future \cite{tso:2013}. The Raspberry is a rather cheap device for 35 euros. This makes it cheaper to do research in compared to a normal server. This is also the mean reason why the Raspberry pi was ones created. The current versions of the Raspberry Pi cannot perform the task of a large scale x86 server \cite{tso:2013}. Building a cloud like this can be a cost effective scale model\cite{tso:2013}. It's a ideal testbed for testing distributed software. During this research we will investigate the performance of a raspberry pi as a video streamer to other computers. The reason I want to investigate it with video streaming is because this demands a lot of bandwidth from the network and could be one of the first things that should be improved.

Today a lot of people watch their movies online using video streaming. 
The Netherlands have for example one million subscribers for Netflix \cite{volkskrant}. Netflix is a video streaming service that makes HD movies watching possible. For this Netflix makes use of a content distribution network (CDN). On the internet this is also known as a on demand service \cite{Adhikari:2012}. Netflix makes use of MPEG-DASH a protocol that makes streaming over http possible \cite{martin:2013}. The problem is that Netflix is responsible for  29.7\% of the peak downstream traffic in US  \cite{Adhikari:2012}. In the Netherlands more and more users are making use of video streaming as Youtube and Netflix. In this research there will be a investigation on the possibility to make small micro data centers with raspberry pi's. This research will try to find out how this cloud works. There will be taken a look in for example the load balancing of video streaming. In this way it can be possible to see improvements that can be made in the load balancing so that the servers can be used more efficient. This is also build to learn more from load balancing and a computer cluster. This can be really useful, because nowadays it's still done on relatively expensive servers.

In this paper we will try to measure the performance of different load balancing techniques using the Raspberry Pi. For this the main research question will be: 
\begin{center}
 What is the performance of a raspberry pi load balancing techniques using video streaming?
\end{center}

In order to come to a good answer we need to  research several things. Therefore several sub-questions will be researched. These sub-questions will altogether provide a answer to the main research question.

\begin{enumerate}
	\item What is small scale cloud computing?
	\item What is cloud video streaming?
	\item What kind of different load balancing techniques are there?
	\item Is it reachable to build small personal Raspberry Pi clouds for services?
	\item Is it possible to improve load balancing using small scale Raspberry Pi's? 
\end{enumerate}

This research will be part literature study and a part of it will be building a small Raspberry Pi cloud to analyze balancing techniques on the Raspberry Pi. For this research cloud video streaming is one of the specific aspects that will be investigated. The load balancing techniques will be optimized for the video streaming. The first three research questions will describe the state of the art. 
The last two sub-questions will go into the technical research that will investigate the performance and possibility of Raspberry Pi's for cloud video streaming. They last one will investigate of their are improvements in load balancing possible. The five sub-questions are being looked at in the next five sections. Followed by a final section for conclusions and identified areas for future
work.

\section{Small scale computing}
Today there are many cloud kinds of cloud computing. The amount of cloud computing services is increasing fast \cite{armbrust:2009}. It's now even possible to build your own small cloud using Raspberry Pi's \cite{southampton}. In this research there will be small scale cloud computing with the Raspberry Pi. The main motivation behind is is that it is ways to expensive to simulate large scale cloud computing. Another reason is the small location that is needed used with small scale cloud computing for Raspberry Pi's\cite{Pcextreme}. The Raspberry Pi is really small compared to a normal server \cite{cox:2014}. Because of this it could be better in executing small tasks. Small scale cloud computing is cloud computing with smaller computation amounts than normal \cite{cox:2014}. More motivation is that it does not use a lot and power.

To understand what small scale cloud computing really is we will look more at the specific cloud service called Infrastructure as a Service:

\section{Video streaming}
There are a lot of cloud services nowadays. These include a webserver, a DNS server, a chat server, a mail server, a vpn server or a monitoring server or even a video streaming service. 
Today a lot of people watch their movies online using video streaming. The netherlands have for example one million subscribers for Netflix \cite{volkskrant}. Netflix is a video streaming service that makes HD movies watching possible. For this Netflix makes use of a content distribution network (CDN). On the internet this is also known as a on demand service. They make use of amazon its AWS with a AWS cloud, Amazon simpleDB , S3 and cassandra for file storage \cite{Adhikari:2012}. Netflix makes use of MPEG-DASH a protocol that makes streaming over http possible. In this research I want to investigate more in the video streaming as a cloud service. 
To investigate this I want to make a experimentation cloud with Raspberry Pi's to see if it will work as a cloud. 
Resources I could use for cloud video streaming:
\cite{g-streamer,raspberry-video,video-1080p, plissonneau:2012}

\section{Load balancing}
In distributed servers it is very important that good load balancing takes place. For this reason I want to further investigate in what kind of load balancing techniques there are. 
Resources I could use for load balancing:
\cite{nginx-load-balancing,nginx-load-balancing-2,computer-networking,wolf:1997,load-balancing}

\section{Raspberry pi}
With this subquestion I want to find out if it is possible to let users have small Raspberry Pi servers I also want to know what the performance of this small Raspberry Pi cloud is. 
Resources:
\cite{Pcextreme,nginx-load-balancing,nginx-load-balancing-2}

For this research I want to investigate if it is possible to do more research in the 
load balancing techniques that can be used in a raspberry pi. A example of this would be the round robin protocol.
Resources:
\cite{nginx-load-balancing,nginx-load-balancing-2}

@@

@@

\section{Conclusion and future work}

\section{Acknowledgments}

### 2015-02-23 research_proposal/research proposal.tex
changes

\maketitle
\begin{abstract}
This document describes a draft research proposal in the
area of cloud computing services. The main research question
is: What is the performance of raspberry pi load balancing service using video streaming? To answer this question a micro raspberry pi video streaming service will be build. 
\end{abstract}

@@

\section{Motivation}
Today there are many cloud services. This amount of cloud computing services is increasing fast \cite{armbrust:2009}.  Despite the attention
from the research community, research and development of
Cloud Computing services is still in it's childhood\cite{tso:2013}. 
In this research the Raspberry Pi cloud services will be investigated. A reason for this is that the density of servers has increased a lot in the past\cite{density}. There are new technologies such as for example the ARM processor. Many companies want to explore the possibilities of for example the Raspberry Pi and his ARM Processor. Some data centers even offer some cloud computing using the Raspberry Pi. A reason for this is the co-location and the low power usage of a Raspberry Pi\cite{hosting,Pcextreme}.  A Raspberry Pi has a power usage between the 3-5 Watt. A normal server has a power usage between the 75 and 150 watt \cite{Powerusage}. This could mean that it is better to use a Raspberry Pi for specific small tasks that do not demand a whole server. During this research I want to further investigate the performance of the Raspberry pi as a server.  A Raspberry Pi can be the small data center for the future \cite{tso:2013}. The Raspberry is a rather cheap device for 35 euros. This makes it cheaper to do research in compared to a normal server. This is also the mean reason why the Raspberry pi was ones created. The current versions of the Raspberry Pi cannot perform the task of a large scale x86 server \cite{tso:2013}. Building a cloud like this can be a cost effective scale model\cite{tso:2013}. It's a ideal testbed for testing distributed software. During this research we will investigate the performance of a raspberry pi as a video streamer to other computers. The reason I want to investigate it with video streaming is because this demands a lot of bandwidth from the network and could be one of the first things that should be improved.

@@

Today a lot of people watch their movies online using video streaming. 
The Netherlands have for example one million subscribers for Netflix \cite{volkskrant}. Netflix is a video streaming service that makes HD movies watching possible. For this Netflix makes use of a content distribution network (CDN). On the internet
this is also known as a on demand service \cite{Adhikari:2012}. Netflix makes use of
MPEG-DASH a protocol that makes streaming over http possible \cite{martin:2013}. The problem is that Netflix is responsible for  29.7\% of the peak downstream traffic in US  \cite{Adhikari:2012}. In the Netherlands more and more users are making use of video streaming as Youtube and Netflix.  In this research we want to investigate if it is possible to make small micro data centers with raspberry pi's. This research will try to find out how this cloud works. There will be taken a look in for example the load balancing of video streaming. In this way it can be possible to see improvements that can be made in the load balancing so that the servers can be used more efficient. This is also build to learn more from load balancing and a computer cluster. This can be really useful, because nowadays it's still done on relatively expensive servers.

\section{Research questions}
The main research question
is: What is the performance of a raspberry pi load balancing service using video streaming?

In order to come to a good answer we need to  research several things

build our own Raspberry Pi setup. There needs to be decided with which benchmark the performance will be measured. After we have measured the performance we can see

\subsection{What is small scale cloud computing?}
In this research I want to do some small scale cloud computing. The main motivation behind is is that it is ways to expensive to simulate large scale cloud computing. Another reason is the Co-location that can be used with small scale cloud computing. Because of this it could be better in executing small tasks. Small scale cloud computing is cloud computing with smaller computation amounts than normal. More motivation is that it does not use a lot of space and power. 
Resources I could use for small scale cloud computing:
\cite{Pcextreme,armbrust:2009,richardson:2012,abrahamsson:2013,southampton}

\subsection{What is cloud video streaming}
There are a lot of cloud services nowadays. These include a webserver, a DNS server, a chat server, a mail server, a vpn server or a monitoring server or even a video streaming service. 
Today a lot of people watch their movies online using video streaming. The netherlands have for example one million subscribers for Netflix \cite{volkskrant}. Netflix is a video streaming service that makes HD movies watching possible. For this Netflix makes use of a content distribution network (CDN). On the internet this is also known as a on demand service. They make use of amazon its AWS with a AWS cloud, Amazon simpleDB , S3 and cassandra for file storage \cite{Adhikari:2012}. Netflix makes use of MPEG-DASH a protocol that makes streaming over http possible. In this research I want to investigate more in the video streaming as a cloud service. 
To investigate this I want to make a experimentation cloud with Raspberry Pi's to see if it will work as a cloud. 
Resources I could use for cloud video streaming:
\cite{g-streamer,raspberry-video,video-1080p, plissonneau:2012}

@@

\subsection{Is it reachable to build small personal Raspberry Pi clouds for services}
With this subquestion I want to find out if it is possible to let users have small Raspberry Pi servers I also want to know what the performance of this small Raspberry Pi cloud is. 
Resources:
\cite{Pcextreme,nginx-load-balancing,nginx-load-balancing-2}

\subsection{Is it possible to improve load balancing using small scale Raspberry Pi's}
For this research I want to investigate if it is possible to do more research in the 
load balancing techniques that can be used in a raspberry pi. A example of this would be the round robin protocol.
Resources:
\cite{nginx-load-balancing,nginx-load-balancing-2}

@@

In this paper there will be research done on making a load balancing service for the Raspberry Pi.  This service will consist of several raspberry Pi's. These Raspberry Pi's make together a small cloud computer.  The Raspberry Pi is made for research and education purposes \cite{raspberry-pi}. The Raspberry Pi is a cheap device costing around 35 euro. It has a power consumption of only three watt and has quite good processor. For this reason it might be very useful for small scale cloud computing. The raspberry Pi is a small device and is excellent for a lot of small devices in a relatively small place. The Raspberry Pi doesn't use cooling and it can be used for very rapid elasticity and on-demand self-service. Because of it's cooling features and low power consumption it might be a good alternative for the nowadays high power consuming data centers. The raspberry pi is really small so it is a lot easier to place extra pi in a data center compared to a normal server. The Raspberry Pi has one drawback and that is that the processing power is relatively low. By using load balancing there will be taken a look at what load balancing techniques are successful for the Raspberry pi.

>>>>

\maketitle
\begin{abstract}
This document describes a draft research proposal in the
area of cloud computing services. The main research question
is: What is the performance of raspberry pi load balancing techniques using video streaming? To answer this question a micro raspberry pi video streaming service will be build. 
\end{abstract}

@@

\section{Motivation}
Today there are many cloud services. This amount of cloud computing services is increasing fast \cite{armbrust:2009}.  Despite the attention
from the research community, research and development of
Cloud Computing services is still in it's childhood\cite{tso:2013}. 
In this research the Raspberry Pi cloud services will be investigated. A reason for this is that the density of servers has increased a lot in the past\cite{density}. There are new technologies such as for example the ARM processor. Many companies want to explore the possibilities of for example the Raspberry Pi and his ARM Processor. Some data centers even offer some cloud computing using the Raspberry Pi. A reason for this is the small location that the Raspberry Pi needs, and the low power usage of a Raspberry Pi\cite{hosting,Pcextreme}.  A Raspberry Pi has a power usage between the 3-5 Watt. A normal server has a power usage between the 75 and 150 watt \cite{Powerusage}. This could mean that it is better to use a Raspberry Pi for specific small tasks that do not demand a whole server. During this research there will be a investigation on the performance of the Raspberry pi as a server.  A Raspberry Pi can be the small data center for the future \cite{tso:2013}. The Raspberry is a rather cheap device for 35 euro. This makes it cheaper to do research in compared to a normal server. This is also the mean reason why the Raspberry pi was ones created. The current versions of the Raspberry Pi cannot perform the task of a large scale x86 server \cite{tso:2013}. Building a cloud like this can be a cost effective scale model\cite{tso:2013}. It's a ideal testbed for testing distributed software. During this research we will investigate the performance of a raspberry pi as a video streamer to other computers. The reason for investigating video streaming is because this demands a lot of bandwidth from the network and could be one of the first things that should be improved.

@@

Today a lot of people watch their movies online using video streaming. 
The Netherlands have for example one million subscribers for Netflix \cite{volkskrant}. Netflix is a video streaming service that makes HD movies watching possible. For this Netflix makes use of a content distribution network (CDN). On the internet this is also known as a on demand service \cite{Adhikari:2012}. Netflix makes use of MPEG-DASH a protocol that makes streaming over http possible \cite{martin:2013}. The problem is that Netflix is responsible for  29.7\% of the peak downstream traffic in US  \cite{Adhikari:2012}. In the Netherlands more and more users are making use of video streaming as Youtube and Netflix.  In this research there will be a investigation on the possibility to make small micro data centers with raspberry pi's. This research will try to find out how this cloud works. There will be taken a look in for example the load balancing of video streaming. In this way it can be possible to see improvements that can be made in the load balancing so that the servers can be used more efficient. This is also build to learn more from load balancing and a computer cluster. This can be really useful, because nowadays it's still done on relatively expensive servers.

\section{Research questions}
The main research question
is: What is the performance of a raspberry pi load balancing techniques using video streaming?

This research will be part literature study and a part of it will be building a small Raspberry Pi cloud to measure balancing techniques on the Raspberry Pi. Here below there are several questions to come to a good answer for the main research question.

\subsection{What is small scale cloud computing?}
In this research there will be small scale cloud computing with the Raspberry Pi. The main motivation behind is that it is ways to expensive to simulate large scale cloud computing. Resources for this:
\cite{southampton, Powerusage, cox:2014}
Another reason is the small location that is needed used with small scale cloud computing for Raspberry Pi's\cite{Pcextreme}. Because of this it could be better in executing small tasks. Small scale cloud computing is cloud computing with smaller computation amounts than normal. More motivation is that it does not use a lot cooling and power. 
Resources available for small scale cloud computing:
\cite{Pcextreme,armbrust:2009,richardson:2012,abrahamsson:2013,southampton}

\subsection{What is cloud video streaming?}
There are many kinds of cloud computing and cloud services. These include a webserver, a DNS server, a chat server, a mail server, a vpn server or a monitoring server or even a video streaming service. 
Information video streaming Netflix:
\cite{volkskrant, Adhikari:2012}
Netflix makes use of MPEG-DASH a protocol that makes streaming over http possible. In this research I want to investigate more in the video streaming as a cloud service.  To investigate what that is are the following resources:
\cite{g-streamer,raspberry-video,video-1080p, plissonneau:2012}

@@

\subsection{Is it reachable to build small personal Raspberry Pi clouds for services?}
With this subquestion I want to find out if it is possible to let users have small Raspberry Pi servers I also want to know what the performance of this small Raspberry Pi cloud is. 
Resources:
\cite{Pcextreme,nginx-load-balancing,nginx-load-balancing-2}

\subsection{Is it possible to improve load balancing using small scale Raspberry Pi's?}
For this research I want to investigate if it is possible to do more research in the 
load balancing techniques that can be used in a raspberry pi. A example of this would be the round robin protocol.
Resources:
\cite{nginx-load-balancing,nginx-load-balancing-2}

@@

The Raspberry Pi is made for research and education purposes \cite{raspberry-pi}. The Raspberry Pi is a cheap device costing around 35 euro. It has a power consumption of only three watt and has quite good processor. For this reason it might be very useful for small scale cloud computing. The raspberry Pi is a small device and is excellent for a lot of small devices in a relatively small place. The Raspberry Pi doesn't use cooling and it can be used for very rapid elasticity and on-demand self-service. Because of it's cooling features and low power consumption it might be a good alternative for the nowadays high power consuming data centers. The raspberry pi is really small so it is a lot easier to place extra pi in a data center compared to a normal server. The Raspberry Pi has one drawback and that is that the processing power is relatively low. By using load balancing there will be taken a look at what load balancing techniques are successful for the Raspberry pi.
